The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-16 exp-resurgence.tex
Finish proving stronger version of thm:has_ae_ODE
This actually gives Borel regularity; just need to change the statement.

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Explain the contents of the section]}
\subsubsection{Regularity results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
\end{equation}
where
\begin{enumerate}
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\color{BlueViolet}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{proof}
After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
\end{proof}
\color{RoyalBlue}
\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

\color{BlueViolet}
Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on appropriate covers of punctured versions of $\C$, like the universal cover $\pi \maps \widetilde{\C^\times} \to \C^\times$.
\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.

\color{RoyalBlue}\textcolor{orange}{[Rephrase more generally, without referring to $P$.} 
$\tilde{\C}$
Choose a root $-\alpha$ of $P$. Consider a simply connected open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ which touches but doesn't contain $\zeta = \alpha$, is star-shaped around $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$. Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it is one-to-one everywhere else.
\color{BlueViolet}
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[violet!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill \p circle (0.7mm);
  }
\end{tikzpicture}
\end{center}
For any $\sigma, \Lambda \in \R$ and $\delta \in [0, 1)$ with $\sigma + \delta \notin \Z$, the intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. The intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i (\sigma + \delta)} - 1)$, so it is closed.
\end{proof}
\begin{theorem}[restatement of \ref{thm:has_ae_ODE}]
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed} \textcolor{orange}{[definition of $\widetilde{B}_{P(-\zeta)}$ should actually be down here]}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

@@

In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself. It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies within the intersection of $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of the latter. The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$. Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.

%%Consider any $\rho > \tau$, recalling our assumption that $\tau > 0$. We know from Propositions \textcolor{orange}{\tt prop:smoothing} 9 and \textcolor{orange}{\tt prop:get-contraction} 10 of \cite{reg-sing-volterra} that $\softpart^\alpha$ maps
%%\[ \singexp{\tau-1}{\Lambda}(\Upsilon) \to \singexp{\tau}{\Lambda}(\Upsilon) \]
%%continuously and $\volterra^\alpha$ contracts $\singexp{\rho-1}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough. Under the same conditions, by working with Taylor series, we can show that $\softpart^\alpha$ maps
%%\[ \zeta^{\tau-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau}\,\mathcal{O}(\pi \Upsilon) \]
%%and $\volterra^\alpha$ maps $\zeta^{\rho-1}\,\mathcal{O}(\pi \Upsilon)$ to itself.
\color{SlateBlue}
\begin{itemize}
\item Prove Theorem~3 using Picard iteration, using the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
given by an arbitary point $b \in \Omega_\alpha$ as our initial guess.
\item This expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, makes it clear that the prototype solution belongs to $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
\item The operator $\volterra^\alpha$ preserves the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$. Hence, the Picard iteration sequence must lie in this subspace.
\item We know from Lemma~\ref{lem:shifted_holo_closed} that the intersection of $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter. Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
\color{SteelBlue}
\item \textbf{[still to do]} Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
\end{itemize}
\color{BlueViolet}

%%Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that

%%Picking an arbitrary point $b \in \Omega_\alpha$, we observe that the {\em prototype solution}
%%\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right] \]

%% \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]

%%Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the subspace

%%The restriction map $\singexp{\sigma}{\Lambda}(\Upsilon) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega_\alpha)$ \textcolor{orange}{\ldots}
The Poincar\'{e} solutions of Equation~\eqref{eq:I} are 1-Gevrey.
This statement is equivalent to Proposition~2.2.1 of \cite{EcalleIII}, proven on p.~114.

@@

where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.

>>>>

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Explain the contents of the section]}
\subsubsection{Regularity results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
\end{equation}
where
\begin{enumerate}
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\color{BlueViolet}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{proof}
After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
\end{proof}
\color{RoyalBlue}
\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

\color{BlueViolet}
Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes. The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.

\color{RoyalBlue}\textcolor{orange}{[Rephrase more generally, without referring to $P$.} 
$\tilde{\C}$
Choose a root $-\alpha$ of $P$. Consider a simply connected open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ which touches but doesn't contain $\zeta = \alpha$, is star-shaped around $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$. Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it is one-to-one everywhere else.
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
For any $\rho' \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma' \in (\rho'-1, \rho']$, the intersection
\[ \zeta^{\rho'}\,\pi^*\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma'}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma'}{\Lambda}(\Upsilon)$.
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma'}{\Lambda}(\Upsilon) \to \singexp{\sigma'}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. The intersection of $\zeta^{\rho'}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma'}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho'} - 1)$, so it is closed.
\textcolor{orange}{[Add flavor text]}
\begin{lemma}\label{lem:laplace-bridge}
\textcolor{orange}{[Move to Laplace transform section?]} Consider an open sector $\Omega$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, but with its tip at $\zeta = 0$. Take some $\rho \in (-1,\infty)$. If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$. \textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. Write $\series{\varphi}$ out in the form
\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
observing that
\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
Taking the Laplace transform of both sides, we learn that
\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.

Proposition~\ref{prop:laplace-cont} tells us \textcolor{orange}{[as long as the opening angle of $\Omega$ is less than $\pi$]} that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray. This, as discussed above, proves the desired result.

%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
\end{proof}
\begin{theorem}[restatement of \ref{thm:has_ae_ODE}]
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

@@

In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself. It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$. The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$. Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.

Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\llbracket \zeta, \zeta^{-1} \rrbracket$. The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\llbracket \zeta \rrbracket$. Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. \textcolor{orange}{[How to rephrase without formal Laplace transform? Conclusion is stronger than statement; change statement accordingly.]}

@@

where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.\color{black}
